\documentclass[a4paper,12pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\pagestyle{fancy}


% Variables
\def\applicationCompany{CTW}
\def\jobName{DevOps Engineer}

\newcommand{\contactInfo}[1]{
	\vspace{-13pt}\item 
	\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
		#1 \\
	\end{tabular*}\vspace{-7pt}
}



\begin{document}
	
	% Contact Info Section 
	\paragraph{\linebreak}
	\paragraph{Michael Hernandez \linebreak
		181 Woodlawn Ct. \linebreak
		Oregon City, OR 97045, USA \linebreak
		\href{mailto:michaelhern@hotmail.com}{\underline{michaelhern@hotmail.com}} \linebreak
		+1 503-380-0710\linebreak} 
	
	\paragraph{\linebreak\today}
	
	\paragraph{Dear Hiring Manager,}
	
	%\paragraph{I am writing to express my strong interest in the \jobName \space position at \applicationCompany.  With my background in software engineering, proficiency in Python and C++, and experience in working with microcontrollers to interface with peripheral sensors, I am confident in my ability to contribute to your team's goal of developing smart and well-designed technical solutions for clients.}
	
	\paragraph{I am excited to apply for the \jobName \space position at \applicationCompany. With my experience in software development, infrastructure management, and experience using tools such as Python, Linux, and Git, I am confident in my ability to contribute to the growth and success \applicationCompany.}
	
	\paragraph{In my current role as a System Validation Engineer at Intel Corporation, I am responsible for post-silicon functional validation of memory controller hardware for Intel Xeon processors.  I successfully debugged failures, identified areas for improvement in test content, and developed validation scripts for use in test suites.  My attention to detail and ability to collaborate with cross-functional teams ensured the identification of bugs and the improvement of product performance.  Furthermore my exprience at Intel has made me comfortable working in a fast-paced environment and thrive in an environment with changing requirements and tight deadlines.}
	
	\paragraph{In addition to my technical qualifications, I have Japanese language proficiency, which will be beneficial in collaborating with Japanese-speaking stakeholders and coworkers.   This versatility allows me to collaborate effectively with development teams and understand their requirements from a broader perspective.}
	
	\paragraph{I am excited about the opportunity to contribute my skills and expertise to your team as a \jobName. I believe that my strong technical background, leadership abilities, and dedication to quality assurance make me an ideal candidate for this position.}
	
	\paragraph{Thank you for considering my application. I would welcome the opportunity to discuss how my skills and experience align with your company's needs in more detail. I look forward to the possibility of joining your team and contributing to the success of your web application projects.}
	
	\paragraph{Sincerely, \linebreak-Michael Hernandez \linebreak}
	
	
\end{document}